---
title: "Text_Mining - Lowest Affordable Housing Loss Rate Zip Code"
author: "Alvin Wendt"
date: "5/14/2021"
output: html_document
---

Read in packages
```{r}
library(tidyverse)
library(tidytext)
library(tidyr)
library(drlib)
library(quanteda)
library(stm)
library(SnowballC)
library(topicmodels)
```

Read in Data and Filter on zips
```{r}
q4_data_raw <- read.csv(file = 'Lowest_Loss_Zip_Codes.csv')

q4_text_zip <- q4_data_raw %>%
    select(propzip, purpose) %>% 
    filter(propzip %in% c(37072, 37013, 37217, 37138, 37211))
    
q4_text_zip
```


```{r}
tidy_q4 <- q4_text_zip %>%
    unnest_tokens(word, purpose) %>%
    anti_join(stop_words) %>% 
    drop_na(word)

tidy_q4$word <- stringr::str_replace_all(tidy_q4$word,"[^a-zA-Z\\s]", " ")

tidy_q4$word <- stringr::str_replace_all(tidy_q4$word,"[\\s]+", "")

tidy_q4 <-  tidy_q4[!(is.na(tidy_q4$word) | is.null(tidy_q4$word) | tidy_q4$word==""| tidy_q4$word==" " | tidy_q4$word=="null"), ]  

tidy_q4 <- tidy_q4 %>% drop_na(word)  %>% 
    filter(!word %in% c("NA", "NULL", "null", "","","a","sf","purpose","construct","attached","permit","type","activity")) # Manual Stop words

# This function lemmatizes words
#tidy_q4 <- tidy_q4 %>%
 # mutate(word = wordStem(word)) 

tidy_q4 %>%
    count(word, sort = TRUE)
```

Run TFIDF on Tidy Data
```{r}
q4_tf_idf <- tidy_q4 %>%
    count(propzip, word, sort = TRUE) %>%
    bind_tf_idf(word, propzip, n) %>%
    arrange(-tf_idf) %>%
    group_by(propzip) %>%
    top_n(15) %>%
    ungroup

q4_tf_idf %>%
    mutate(word = reorder_within(word, tf_idf, propzip)) %>%
    ggplot(aes(word, tf_idf, fill = propzip)) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ propzip, scales = "free", ncol = 3) +
    scale_x_reordered() +
    coord_flip() +
    theme(strip.text=element_text(size=11)) +
    labs(x = NULL, y = "tf-idf",
         title = "Highest tf-idf words in Nashville Zip Code")

```

Cast data in DocumentTermMatrix format
```{r}
q4_dfm <- tidy_q4 %>%
    count(propzip, word, sort = TRUE) %>%
    cast_dfm(propzip, word, n)

q4_sparse <- tidy_q4 %>%
    count(propzip, word, sort = TRUE) %>%
    cast_sparse(propzip, word, n)

```


Create Estimation of the Structural Topic Models for various number of topics
```{r}
topic_model6 <- stm(q4_dfm, K = 6, 
                   verbose = FALSE, init.type = "Spectral")

topic_model5 <- stm(q4_dfm, K = 5, 
                   verbose = FALSE, init.type = "Spectral")

topic_model4 <- stm(q4_dfm, K = 4, 
                   verbose = FALSE, init.type = "Spectral")

topic_model3 <- stm(q4_dfm, K = 3, 
                   verbose = FALSE, init.type = "Spectral")

topic_model2 <- stm(q4_dfm, K = 2, 
                   verbose = FALSE, init.type = "Spectral")


```

Graph beta parameter of the Dirichlet on the per-topic word distribution for 6 topics
```{r}
td_beta <- tidy(topic_model6)

td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "Highest word probabilities for each topic",
         subtitle = "Different words are associated with different topics")

```

Graph gamma parameter of the Dirichlet on the per-document-per-topic matrix word distribution for 6 topics
```{r}
td_gamma <- tidy(topic_model6, matrix = "gamma",                    
                 document_names = rownames(q4_dfm))

ggplot(td_gamma, aes(gamma, fill = as.factor(topic))) +
  geom_histogram(alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~ topic, ncol = 3) +
  labs(title = "Distribution of document probabilities for each topic",
       y = "Number of Zip codes", x = expression(gamma))

```

Graph beta and gamma parameters of the Dirichlet on the per-topic and per-document-per-topic matrix word distribution for 5 topics
```{r}
td_beta <- tidy(topic_model5)

td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "Highest word probabilities for each topic",
         subtitle = "Different words are associated with different topics")

td_gamma <- tidy(topic_model5, matrix = "gamma",                    
                 document_names = rownames(q4_dfm))

ggplot(td_gamma, aes(gamma, fill = as.factor(topic))) +
  geom_histogram(alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~ topic, ncol = 3) +
  labs(title = "Distribution of document probabilities for each topic",
       y = "Number of Zip codes", x = expression(gamma))

```

Graph beta and gamma parameters of the Dirichlet on the per-topic and per-document-per-topic matrix word distribution for 4 topics
```{r}
td_beta <- tidy(topic_model4)

td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "Highest word probabilities for each topic",
         subtitle = "Different words are associated with different topics")

td_gamma <- tidy(topic_model4, matrix = "gamma",                    
                 document_names = rownames(q4_dfm))

ggplot(td_gamma, aes(gamma, fill = as.factor(topic))) +
  geom_histogram(alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~ topic, ncol = 3) +
  labs(title = "Distribution of document probabilities for each topic",
       y = "Number of Zip codes", x = expression(gamma))

```

Graph beta and gamma parameters of the Dirichlet on the per-topic and per-document-per-topic matrix word distribution for 3 topics
```{r}
td_beta <- tidy(topic_model3)

td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "Highest word probabilities for each topic",
         subtitle = "Different words are associated with different topics")

td_gamma <- tidy(topic_model3, matrix = "gamma",                    
                 document_names = rownames(q4_dfm))

ggplot(td_gamma, aes(gamma, fill = as.factor(topic))) +
  geom_histogram(alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~ topic, ncol = 3) +
  labs(title = "Distribution of document probabilities for each topic",
       y = "Number of Zip codes", x = expression(gamma))

```
Graph beta and gamma parameters of the Dirichlet on the per-topic and per-document-per-topic matrix word distribution for 2 topics
```{r}
td_beta <- tidy(topic_model2)

td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "Highest word probabilities for each topic",
         subtitle = "Different words are associated with different topics")

td_gamma <- tidy(topic_model2, matrix = "gamma",                    
                 document_names = rownames(q4_dfm))

ggplot(td_gamma, aes(gamma, fill = as.factor(topic))) +
  geom_histogram(alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~ topic, ncol = 3) +
  labs(title = "Distribution of document probabilities for each topic",
       y = "Number of Zip codes", x = expression(gamma))
```


# Latent Dirichlet allocation

Latent Dirichlet allocation
```{r}
ap_lda <- LDA(q4_dfm, k = 2, control = list(seed = 1234))
ap_lda
```

Extracting the per-topic-per-word probabilities or Beta
```{r}
ap_topics <- tidy(ap_lda, matrix = "beta")
ap_topics
```

Top 10 terms that are most common within each topic
```{r}
ap_top_terms <- ap_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```


```{r}
beta_wide <- ap_topics %>%
  mutate(topic = paste0("topic", topic)) %>%
  pivot_wider(names_from = topic, values_from = beta) %>% 
  filter(topic1 > .001 | topic2 > .001) %>%
  mutate(log_ratio = log2(topic2 / topic1))


beta_wide
```

```{r}
ap_documents <- tidy(ap_lda, matrix = "gamma")
ap_documents
```

Latent Dirichlet allocation
```{r}
ap_lda <- LDA(q4_dfm, k = 3, control = list(seed = 1234))
ap_lda
```

Extracting the per-topic-per-word probabilities or Beta
```{r}
ap_topics <- tidy(ap_lda, matrix = "beta")
ap_topics
```

Top 10 terms that are most common within each topic
```{r}
ap_top_terms <- ap_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```


Latent Dirichlet allocation
```{r}
ap_lda <- LDA(q4_dfm, k = 4, control = list(seed = 1234))
ap_lda
```
Extracting the per-topic-per-word probabilities or Beta
```{r}
ap_topics <- tidy(ap_lda, matrix = "beta")
ap_topics
```

Top 10 terms that are most common within each topic
```{r}
ap_top_terms <- ap_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```


Latent Dirichlet allocation
```{r}
ap_lda <- LDA(q4_dfm, k = 5, control = list(seed = 1234))
ap_lda
```

Extracting the per-topic-per-word probabilities or Beta
```{r}
ap_topics <- tidy(ap_lda, matrix = "beta")
ap_topics
```

Top 10 terms that are most common within each topic
```{r}
ap_top_terms <- ap_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```


Latent Dirichlet allocation
```{r}
ap_lda <- LDA(q4_dfm, k = 6, control = list(seed = 1234))
ap_lda
```

Extracting the per-topic-per-word probabilities or Beta
```{r}
ap_topics <- tidy(ap_lda, matrix = "beta")
ap_topics
```

Top 10 terms that are most common within each topic
```{r}
ap_top_terms <- ap_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```


